---
title: "Shiny Application and Reproducible Pitch"
author: "Mohamed Adel Omar"
date: "8/18/2020"
output: ioslides_presentation
runtime: shiny
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

<!-- ## Assignment  -->

<!-- - Write a shiny application with associated supporting documentation.   -->
<!-- - The documentation should be thought of as whatever a user will need to get started using your application.   -->
<!-- - Deploy the application on Rstudio's shiny server.   -->
<!-- - Share the application link by pasting it into the provided text box.    -->
<!-- - Share your server.R and ui.R code on github document.   -->

## Shiny Application 

- We using the mtcars dataset to cluster between two columns.  
- The user can select between multiple mtcars columns.  
- The user can select the number of clusters (1 to 15).  
- Every cluster have different color.   
- You can Choose columns  that you want: Cylinders, Horse Power and Transmission Quater Mile Time.  
  
Example in Shiny Apps:- https://madel.shinyapps.io/assignmentapp/    
The code in Github :- https://github.com/madelomer/Assignment9  

## Interactive Application

```{r mtcars}

vars <- setdiff(names(mtcars), "Species")

pageWithSidebar(
  headerPanel('mtcars k-means clustering'),
  sidebarPanel(
    selectInput('xcol', 'X Variable', vars),
    selectInput('ycol', 'Y Variable', vars, selected = vars[[2]]),
    numericInput('clusters', 'Cluster count', 3, min = 1, max = 15)
  ),
  mainPanel(
    plotOutput('plot1')
  )
)

  selectedData <- reactive({
    mtcars[, c(input$xcol, input$ycol)]
  })
  
  clusters <- reactive({
    kmeans(selectedData(), input$clusters)
  })
  output$plot1 <- renderPlot({
    palette(c("#E41A1C", "#377EB8", "#4DAF4A", "#984EA3",
              "#FF7F00", "#FFFF33", "#A65628", "#F781BF", "#999999",
              "#DAF7A6", "#FFC300", "#FF5733","#C70039","#900C3F","#581845"))
    
    par(mar = c(5.1, 4.1, 0, 1))
    plot(selectedData(),
         col = clusters()$cluster,
         pch = 20, cex = 3)
    points(clusters()$centers, pch = 4, cex = 4, lwd = 4)
  })
  

```


##  UI code 

```{r ui, eval=FALSE,echo=TRUE}

vars <- setdiff(names(mtcars), "Species")

pageWithSidebar(
  headerPanel('mtcars k-means clustering'),
  sidebarPanel(
    selectInput('xcol', 'X Variable', vars),
    selectInput('ycol', 'Y Variable', vars, selected = vars[[2]]),
    numericInput('clusters', 'Cluster count', 3, min = 1, max = 15)
  ),
  mainPanel(
    plotOutput('plot1')
  )
)
```

## Server Code
```{r server, eval=FALSE,echo=TRUE}
 selectedData <- reactive({ mtcars[, c(input$xcol, input$ycol)]})
  clusters <- reactive({ kmeans(selectedData(), input$clusters) })
  output$plot1 <- renderPlot({
    palette(c("#E41A1C", "#377EB8", "#4DAF4A", "#984EA3","#FF7F00", "#FFFF33", "#A65628", "#F781BF","#999999","#DAF7A6", "#FFC300", "#FF5733","#C70039", "#900C3F","#581845"))
    par(mar = c(5.1, 4.1, 0, 1))
    plot(selectedData(),
         col = clusters()$cluster, pch = 20, cex = 3)
    points(clusters()$centers, pch = 4, cex = 4, lwd = 4)
  })
```
**$Thank$**      **$You$**

